Covariate analysis of ROSMAP RNASeq

### 2016-02-09 code/Rmd/ROSMAP_RNASeq.Rmd
Minor bug fix in ROSMAP RNASeq processing

# Match covariates to expression data
rownames(METADATA) = METADATA$Sampleid
METADATA = METADATA[indToRetain,]
```
Dorsolateral prefrontal cortex of `r dim(EXPR)[2]` subjects from the ROS and MAP cohorts were obtained from AMP-AD portal

>>>>

# Match covariates to expression data
rownames(METADATA) = METADATA$Sampleid
METADATA = METADATA[indToRetain,]

# Arrange rows of metadata in the same order as columns of expression
METADATA = METADATA[colnames(EXPR),]
```
Dorsolateral prefrontal cortex of `r dim(EXPR)[2]` subjects from the ROS and MAP cohorts were obtained from AMP-AD portal
